%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Change the font size of your document - 10pt, 12.1pt, etc.
\documentclass[letterpaper,11pt,oneside]{article}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage[colorlinks]{hyperref}
%\usepackage{stix}
\usepackage{graphicx}
\graphicspath{ {images/}} %upload your signature to this file
%Change the margins to fit your CV/resume content
\usepackage[left=1in, right=1in, bottom=1.25in, top=1.25in]{geometry}

%Skype information - include your Skype name for a link to add you on Skype

%Changes the page numbers - {arabic}=arabic numerals, {gobble}=no page numbers, {roman}=Roman numerals
\pagenumbering{gobble}
\hypersetup{
    urlcolor = blue,
}

%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%%%%%%

\begin{document}
\noindent
\textbf{\Large{Chun Yui (Nicholas) Wong}}
\vspace{0.5cm}\\
\noindent
Department of Engineering, University of Cambridge\\
Email: \href{mailto:cyw28@cam.ac.uk}{\texttt{cyw28@cam.ac.uk}}\\
Address: Jesus College, Cambridge, U.K.\\
Links: \href{https://scholar.google.com/citations?user=uKp2t5EAAAAJ&hl=en}{Google Scholar}, \href{https://www.researchgate.net/profile/Chun_Yui_Wong}{ResearchGate}
\section*{Education}
\begin{itemize}
\item \textbf{2021 (expected)}: PhD, Computational Design, University of Cambridge\\
Supervisor: Dr. Geoffrey T. Parks, Dr. Pranay Seshadri
\begin{itemize}
\item Project title: \emph{Dimension Reduction Ideas for Scalable and Efficient Robust Design Paradigms in Turbomachinery}
\end{itemize}
\item \textbf{2018}: B.A./M.Eng (Hons.), Information and Computer Engineering, University of Cambridge
\begin{itemize}
\item Class I, within 3rd percentile of year group of 300 for part IA, IB and IIA.
\item Final Year Project: \emph{Polynomial Approximations and Sensitivity Analysis via Compressed Sensing}
\end{itemize}
\end{itemize}

\section*{Scholarships and Awards}
\begin{itemize}
\item \textbf{2018}: Cambridge Trusts Scholarship 
\item \textbf{2018}: Lloyds Register Foundation Award (via the Alan Turing Institute)
\item \textbf{2018}: Hogwood Scholarship, Jesus College, Cambridge
\item \textbf{2018}: Funding from Rolls Royce plc. 
\item \textbf{2018}: Kelly Prize for the Engineering Tripos
\item \textbf{2017}: College Prize and Scholarship for Part IIA Engineering
\item \textbf{2016}: Benefactor’s and Engineers’ Prize for Part IB Engineering
\item \textbf{2015}: Evans Prize and Scholarship for Part IA Engineering
\item \textbf{2014}: Silver award at the 45th International Physics Olympiad
\item \textbf{2014}: Honourable mention at the 14th Asian Physics Olympiad Olympiad
\item \textbf{2011}: Silver award at the 8th International Junior Science Olympiad
\end{itemize}

\section*{First Authored Publications and Presentations}
\begin{itemize}
\item \textbf{Wong, C. Y.}, Seshadri, P., Parks, G. T., Girolami, M., Embedded Ridge Approximations. \emph{Computer Methods in Applied Mechanics and Engineering} 372 (2020) 113383 \href{https://doi.org/10.1016/j.cma.2020.113383}{Paper}  \href{https://arxiv.org/abs/1907.07037}{Preprint}. 
\begin{itemize}
\item Poster presented at FrontUQ workshop in Pisa, Italy. 
\item Contributed lecture accepted at SIAM UQ20 conference in Munich, Germany. (Canceled due to pandemic)
\end{itemize}

\item \textbf{Wong, C. Y.}, Seshadri, P., Parks, G. T., (2021) Extremum sensitivity analysis with polynomial Monte Carlo filtering. \emph{Reliability Engineering and Systems Safety} 212 (2021) 107609. \href{https://doi.org/10.1016/j.ress.2021.107609}{Paper} \href{https://arxiv.org/abs/1907.08113}{Preprint}.

\item \textbf{Wong, C. Y.}, Seshadri, P., Parks, G. T., Blade Envelopes \href{https://arxiv.org/abs/2011.11636}{Preprint Part I} \href{https://arxiv.org/abs/2012.15579}{Preprint Part II}

\item  \textbf{Wong, C. Y.}, Seshadri, P., Parks, G. T., Automatic Borescope Damage Assessments for Gas Turbine Blades via Deep Learning \href{https://doi.org/10.2514/6.2021-1488}{Conference paper} \href{https://arxiv.org/abs/2103.05430}{Preprint} 
\begin{itemize}
\item Presented at AIAA SciTech Forum and Exposition 2021.
\end{itemize}

\end{itemize}

\section*{Work Experience}
\begin{itemize}
\item \textbf{2017-Present}: Developer at \href{https://www.effective-quadratures.org/}{\emph{Effective Quadratures}}
\begin{itemize}
\item Giving regular workshop tutorials exposing the capabilities related to supervised machine learning using the code. Locations include:
\begin{itemize}
\item Rolls Royce plc. Derby, U.K.
\item UK Atomic Energy Authority, Culham, U.K.
\end{itemize}
\item Coded up routines for least-squares regression and compressed sensing recovery of orthogonal polynomial approximation models.
\item Coded up routines for subspace-based dimension reduction.
\item Developing unit tests for numerical methods.
\end{itemize}
\item \textbf{Summer 2020}: Mentor for Google Summer of Code at \emph{NumFocus}
\begin{itemize}
\item Project: Orthogonal polynomial regression trees in Effective Quadratures
\end{itemize}

\item \textbf{2018}: Cambridge Mathematics Placement at the Department of Biochemistry, University of Cambridge
\begin{itemize}
\item Developed techniques related to $\ell_1$ minimization to recover NMR scan data from incomplete time-domain samples.
\end{itemize}
\item \textbf{2017}: Undergraduate research project at Machine Intelligence Lab, Department of Engineering, Cambridge
\begin{itemize}
\item Designed Python user interface for C++ library for label propagation in computer vision.
\item Improved functionality of library to handle wider range of image sequences more quickly.
\end{itemize}
\item \textbf{2016}: Software engineering internship at ASM Pacific Technology, Hong Kong
\begin{itemize}
\item Implemented unit tests for existing library functions for actuating an ultrasonic transducer.
\item Improved GUI for mobilizing the library with usability tests.
\item Developed new interface for monitoring I/O ports with C\# and XAML in Visual Studio.
\end{itemize}
\item \textbf{2015}: Undergraduate research project at Centre of Smart Infrastructure, CUED
\begin{itemize}
\item Coded AVR controller for collecting data using a tilt sensor.
\end{itemize}

\end{itemize}

\section*{Teaching}
\begin{itemize}
\item 2P7 Vector Calculus: Michaelmas 2019
\item 3M1 Mathematical Methods: Lent 2020, Lent 2019
\item 1P4 Mechanical Vibrations: Easter 2019
\end{itemize}

\section*{Extra-curricular Activities}
\begin{itemize}

\item \textbf{2015-16}: President/Director of Cambridge University Chinese Orchestra Society
\begin{itemize}
\item Responsible for overseeing the operation of the orchestra, including managing rehearsals, performances, sponsorship and promotions.
\item Hosting annual concert attended by around 150 people.
\end{itemize}
\item \textbf{2014}: Editor for 64th annual mathematical magazine Eureka for the Archimedeans society at Cambridge
\begin{itemize}
\item Editing technical articles using Adobe InDesign.
\end{itemize}
\item \textbf{2012-13}: Instructor and leader of school physics Olympiad team

\end{itemize}

\section*{Skills and Languages}
\begin{itemize}
\item \textbf{Computer Programming}: Python, C++, C, MATLAB, C\#/XAML. Basic Linux skills.
\item \textbf{Languages}: Native Cantonese/Mandarin Chinese. Fluent English. Elementary Japanese.
\end{itemize}

\end{document}

